Building a Probabilistic Model with Deep Neural Networks for Camera Geo-Calibration

### 2018-07-01 chapters/introduction/introduction.tex
minor change

As one of the primary vision tasks, camera calibration plays an
important role in many applications like autonomous driving, indoor
layout estimation and image mensuration. 
In the camera pin-hole model, the projection from scene to the image
frame are determined by camera intrinsic and extrinsic parameters. 
The intrinsic parameters describe the information of camera
itself such as focal length, principal point \etc; 
The extrinsic parameters describe the external states of the
camera, such as the camera poses and translation under some
coordinate system.
Some applications like GIS and geo-localization are more interested in
calibrating the camera under geographic coordinates, namely knowing
the camera pose with respect to the ground reference frame (\ie ENU)
and camera location in geographic coordinates. We refer to such
calibration as \textbf{geo-calibration}.
In this work, our study mainly focuses on estimating geo-calibration
extrinsic parameters like camera pose and the
geo-orientation/geo-localization of the camera.

In current work of camera calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also forebear the following
drawbacks: 1) Deterministic systems can not handle uncertainties which
are commonly encountered in the real world problems.  2) Deterministic
systems are not friendly to applications developed with graphic models
that are interfaced with their outputs.
To address these drawbacks, We propose to build probabilistic
models for camera geo-calibration.

A complete geo-calibration detects both camera intrinsic (focal length,
principal points \etc) and extrinsic parameters, which includes camera
roll, pitch angles, geographic orientation and geographic locations.
In our work, we first build a probabilistic model to detect multiple
geo-calibration parameters jointly. Our algorithm construct a set of
constraint functions to measure the fitness between the
geo-calibration parameters and the observations. An energy function
is constructed with these constraint functions. Thus each point in the
solution space forebear a energy score (proportional to the
probability at that point). We then use graphic model approach to
sample these point in the space.

In recent years, deep neural networks (DNNs) rise as stars in recent
years. Methods that uses DNNs achieve state-of-the-art performances in
many computer vision areas (\todo{citations}). We demonstrate that
DNNs are good tools to solve the calibration problems. 
As a next step of our study, We further
divide these constraints on subset of the calibration parameters and
conquer them with DNNs.

We first focus on camera roll and pitch angles. Given the already
known intrinsic parameters, camera roll and pitch angles can be
derived from the horizon line position in the image. Detecting horizon
line is easier because it is tightly related to the content/appearance
of the scene. In our work, we create a new method to use DNNs to give
a prior distribution of the horizon line, then assign a probability to
each by measuring their consistences with vanishing points detected
with traditional statistic methods.

Study of geo-localization has a long history. \todo{citations}. We
seek to geo-localize images with temporal information. The system
estimate the geographic location of the camera in the form of discrete
probabilities over bins. This application works in rough scale. We
also design another algorithm that can do finer scale localization
based on the rough location input. In that work, we train a network to
transfer the semantic segmentation masks from the top-view perspective
to the ground view perspective. In order to train the network, we have
to construct the image pairs called cross-view image pairs.

Overhead imagery plays an import role in the cross-view learning area.
To construct a cross view image pair, we need to know the geographic
location (sometimes also with the geographic orientation).
\todo{copy from scott} Efforts have been made to
automate overhead image analysis. As early as
1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.

Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options. With
the geographic information of the ground image, we are able to
download the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.

Our algorithm takes advantage of cross-view pairs, to train a deep
neural network that can semantically segment the overhead image and
then transfer the segmentation mask to the ground view. To finer
geo-orient and localize the image, we can match the ground
segmentation mask with the mask generated from overhead image at
location $l$.

Another contribution of our work is that along the training for
networks that do geo-calibration, we are able to learn to extract
high-level features from the networks along side.

>>>>

As one of the primary vision tasks, camera calibration plays an
important role in many applications like autonomous driving, indoor
layout estimation and image mensuration. 
In the camera pin-hole model, the projection from scene to the image
frame are determined by camera intrinsic and extrinsic parameters. 
The intrinsic parameters describe the information of camera
itself such as focal length, principal point \etc; 
The extrinsic parameters describe the external states of the
camera, such as the camera poses and translation under some
coordinate system.
Some applications like GIS and geo-localization are more interested in
calibrating the camera under geographic coordinates, namely knowing
the camera pose with respect to the ground reference frame (\ie ENU)
and camera location in geographic coordinates. We refer to such
calibration as \textbf{geo-calibration}.
The complete geo-calibration includes intrinsic (focal
length, principal points \etc) and extrinsic parameters.
In this work, our study mainly focuses on estimating geo-calibration
extrinsic parameters like camera pose and the
geo-orientation/geo-localization of the camera.

In current work of camera calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also forebear the following
drawbacks: 1) Deterministic systems can not handle uncertainties which
are commonly encountered in the real world problems.  2) Deterministic
systems are not friendly to applications developed with graphic models
that are interfaced with their outputs.
To address these drawbacks, We propose to build probabilistic
models for camera geo-calibration.
We first build a probabilistic model to detect multiple
geo-calibration parameters jointly.  Our algorithm treats each set of
geo-calibration parameters as a point in the solution space. It
constructs an energy function for points in the solution space to
measure the fitness between the geo-calibration parameters and the
observations (images), so that each point is associated with an energy
score.  The probability over the calibration parameters is
anti-proportional to the energy score, which we then compute with
graphic model approach. The essential part of our algorithm is the
construction of the energy function. To better measure the fitness
between the calibration parameters and the observation, we divide the
energy function into a combination of partial calibration problems,
each of which is responsible for a subset of calibration parameters.
We will discuss these constraint functions in several following work.

In recent years, deep neural networks (DNNs) rise as stars. Methods
using DNNs achieve state-of-the-art performances in
many computer vision areas (\todo{citations}). We demonstrate that
DNNs are good tools to solve partial calibration problems. 
As a next step of our study, We focus on calibrating cameras with deep
neural networks.

We first estimate camera roll and pitch angles. Assuming the intrinsic
parameters are known, camera roll and pitch angles can be
derived from the horizon line position in the image. Detecting horizon
line is easier because it is tightly related to the content/appearance
of the scene. In our work, we first create a new method using DNNs to
give a prior distribution of the horizon line, then assign a
probability to each by measuring their consistences with vanishing
points detected using traditional statistic methods.

Study of geo-localization has a long history. \todo{citations}. In
another work, We seek to geo-localize images with temporal
information. The system estimates the discrete probability over the
camera geographic location. This application works in rough scale. In
our next work, we design an algorithm that can do fine-scale localization
based on the rough geographic location inputs. In that work, we
designed a deep neural network to transfer the semantic segmentation
masks from the top-view perspective to the ground view perspective. In
order to train the network, we have to construct a data form called
cross-view image pairs.

Overhead imagery plays an import role in the cross-view learning area.
To construct a cross view image pair, we need to know the geographic
location (sometimes also with the geographic orientation).
\todo{rewrite the following} Efforts have been made to
automate overhead image analysis. As early as
1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.

Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
download the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.

%Our algorithm takes advantage of the cross-view pairs, to train a deep
%neural network that can semantically segment the overhead image and
%then transfer the segmentation mask to the ground view. To finer
%geo-orient and localize the image, we can match the ground
%segmentation mask with the mask generated from overhead image at
%location $l$.

Another contribution of our work is that along the training for
networks that do geo-calibration, we are able to learn to extract
high-level features from the networks. \todo{expand}
